### 2023-12-22 paper_interaction_conf/main.tex
Add LaTeX files for paper_interaction_conf

%%
%% Interaction 2024 Technical Report Submission
%% V1.0 (2023/12/22)
%%

\documentclass[submit,techrep,english]{ipsj}

\usepackage{graphicx}
\usepackage{latexsym}

\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}

\setcounter{volume}{64}%vol53=2012
\setcounter{number}{10}
\setcounter{page}{1}

% インタラクション特有の設定。印刷工程で柱・ノンブルの埋め込みを行う。
\makeatletter
\pagestyle{empty}
\def\@oddhead{}%
\def\@evenhead{}%
\def\ps@IPSJTITLEheadings{}
\makeatother

\begin{document}

\title{MyStoryKnight: A Character-drawing Driven Storytelling System Using LLM Hallucinations}

\affiliate{LU}{Lund University}
\affiliate{TUD}{Technical University of Denmark}
\affiliate{HRI}{Honda Research Institute Japan}
\affiliate{UTokyo}{The University of Tokyo}
\paffiliate{PUTokyo}{The University of Tokyo}

\author{Yotam Sechayk}{UTokyo}[sechayk-yotam@g.ecc.u-tokyo.ac.jp]
\author{Isa A. Randsalu}{LU,PUTokyo}[randsalu-isa071@g.ecc.u-tokyo.ac.jp]
\author{Gabriela A. Penarska}{TUD,PUTokyo}[gabriela-penarska@g.ecc.u-tokyo.ac.jp]
\author{Christian Arzate Cruz}{HRI}[]
\author{Takeo Igarashi}{UTokyo}[]

\begin{abstract}
    Test.
\end{abstract}

\maketitle

%1
\section{Introduction}

%2
\section{Related Work}

%3
\section{System Overview}

%4
\section{Implementation}

%5
\section{Evaluation}

%6
\section{Discussion}

%7
\section{Conclusion}

% Acknowledgment
\begin{acknowledgment}
    Test.
\end{acknowledgment}

% Bibliography
\bibliographystyle{ipsjsort-e}
\bibliography{references}

% Appendix
\appendix

\end{document}

### 2023-12-22 paper_interaction_conf/main.tex
Add new images and update bibliography

@@
 \author{Yotam Sechayk}{UTokyo}[sechayk-yotam@g.ecc.u-tokyo.ac.jp]
+\author{Gabriela A. Penarska}{TUD,PUTokyo}[gabriela-penarska@g.ecc.u-tokyo.ac.jp]
 \author{Isa A. Randsalu}{LU,PUTokyo}[randsalu-isa071@g.ecc.u-tokyo.ac.jp]
-\author{Gabriela A. Penarska}{TUD,PUTokyo}[gabriela-penarska@g.ecc.u-tokyo.ac.jp]
 \author{Christian Arzate Cruz}{HRI}[]
+
 \author{Takeo Igarashi}{UTokyo}[]
@@
 \begin{abstract}
-    Test.
+    Storytelling is a valuable tradition that plays a crucial role in child development, fostering creativity and a sense of agency.
+However, many parents struggle to engage in interactive storytelling due to various constraints.
+As a result, children often consume stories passively, missing out on the opportunity to participate in the creative process.
+To address this, we propose MyStoryKnight, a character drawing driven storytelling system.
+By leveraging LLM hallucinations, our system generates adventure-type stories that allow users to navigate and make choices.
+Through a complexity analysis algorithm, we ensure the coherence and consistency of the generated stories, resulting in engaging and easily comprehensible narratives.
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:introduction}
+
+Creativity is increasingly recognized as a crucial aspect of the modern working environment.
+In the context of child development, creativity plays a pivotal role in fostering learning and growth \cite{1:ElgarfP22}, which extends to adulthood.
+As a result, there has been a growing interest in leveraging creative artificial intelligence (AI) and exploring the use of AI agents to stimulate children's creativity.
+Previous research has demonstrated the positive effects of incorporating AI agents with creative abilities in enhancing children's creative thinking \cite{1:ElgarfP22}.
+Additionally, the use of storytelling robots and virtual characters as interactive tools has gained traction in recent years \cite{7:SunLLL17}.
+These advancements highlight the potential of AI technologies in promoting and nurturing creativity in children, thereby shaping their cognitive and emotional development.
+
+One effective way to promote creativity is through storytelling, a popular activity for entertaining and bonding with children \cite{7:SunLLL17}.
+Storytelling plays a crucial role in child development \cite{9:RyokaiC99} and offers several ultiple benefits \cite{7:SunLLL17}.
+Both story-making and storytelling contribute to the development of verbal and social skills \cite{1:ElgarfP22}, and recent research suggests that storytelling broadens vocabulary, improves narrative comprehension, and accelerates cognitive development in children \cite{7:SunLLL17}.
+Creating fictional worlds and characters helps children improve their language skills, both in comprehension and usage \cite{13:abs-2011-04242}.
+
+Collaborative storytelling has been shown to be an effective way of building and strengthening relationships \cite{8:ShakeriND21}, also playing an important role in parent-child bonding \cite{12:ZhangXWYRWYWL22}.
+Interactive stories stimulate children's thinking and imagination \cite{11:LimaGV20}, and help children make sense of their world through shared experiences \cite{9:RyokaiC99}.
+Despite these benefits, many parents do not regularly engage in interactive storytelling with their children due to limited availability, time, or energy [7, 12].
+
+To address this, we propose \textbf{MyStoryKnight}, a character drawing driven storytelling system that uses LLM hallucinations to generate an adventure-type story with user agency and navigation.
+Our system uses drawings of characters as input, and generates an unfolding story that the user can navigate through based on their choices.
+Using a complexity analysis algorithm, we guide the LLM hallucinations to generate a coherent and consistent story.
+Resulting in a story that is both engaging and easy to follow.
+
+Our contributions are:
+\begin{itemize}
+    \item Storytelling system that uses the character drawing as a basis for the story.
+    \item LLM hallucinations to generate an adventure-type story with user navigation.
+    \item Complexity analysis of story generation for coherency and consistency.
+\end{itemize}
 
@@
 \section{Related Work}
+\label{sec:related-work}
+
+Previous works have explored using interactive dialogue to develop congruent stories, utilizing online information to enrich narratives \cite{13:abs-2011-04242}, creating storytelling experiences with interactive questioning and answering through collaboration between parents and AI \cite{12:ZhangXWYRWYWL22}, and input and personalization have been used to make stories more engaging and informative \cite{14:WangRCRMB22}.
+Research has also focused on enhancing collaborative storytelling between friends and how AI can promote curiosity and discovery by hallucinating new details \cite{8:ShakeriND21}.
+Other studies have considered interaction with existing characters \cite{10:ChopraVSS21}, image-based storytelling with non-verbal prompt generation \cite{4:HanC23}, controlling characters through physical gestures \cite{2:LiuLWCS12}, and physical body engagement \cite{3:ZhaoB23}.
+The possibility of using sketches to influence character behavior or affect the plot of a story, allowing users to interact with narratives by sketching objects, has also been explored \cite{11:LimaGV20}.
+Multi-modal systems, combining oral narration, visual images, and body engagement \cite{3:ZhaoB23}, and systems using user input in the form of prompts to have AI generate high-quality images for story creation \cite{4:HanC23} are also examples of prior works.
+
+Previous studies suggest that many current interactive AI systems lack the ability to encourage children's enthusiasm.
+It has also been shown that interesting stories often involve narrative shifts and that interactive narratives do not have to be strictly straightforward or logical.
+However, it is crucial to maintain some elements that remain constant, such as character and location descriptions \cite{13:abs-2011-04242}.
+
+Achieving high child engagement is a critical factor in interactive storytelling \cite{12:ZhangXWYRWYWL22}.
+Challenges in interactive storytelling include the difficulty of maintaining a child's attention, especially when there is little change in activities or interaction patterns \cite{13:abs-2011-04242}.
+Narrators must respond in a way that keeps the child interested while maintaining the narrative trajectory.
+Children quickly become bored and distracted, and in terms of storytelling, it's an issue that becomes more problematic when the parent is not present \cite{12:ZhangXWYRWYWL22}.
+Another crucial factor in storytelling is the story characters, and providing users with the possibility to interact with characters can offer a more immersive and informative experience \cite{10:ChopraVSS21}.
+Interactivity and authorship, where computational methods allow users to participate in story creation, are fundamental aspects of interactive storytelling \cite{11:LimaGV20}.
 

### 2023-12-22 paper_interaction_conf/main.tex
Refactor storytelling system to generate interactive stories using character drawings

@@
     Storytelling is a valuable tradition that plays a crucial role in child development, fostering creativity and a sense of agency.
-However, many parents struggle to engage in interactive storytelling due to various constraints.
-As a result, children often consume stories passively, missing out on the opportunity to participate in the creative process.
-To address this, we propose MyStoryKnight, a character drawing driven storytelling system.
-By leveraging LLM hallucinations, our system generates adventure-type stories that allow users to navigate and make choices.
-Through a complexity analysis algorithm, we ensure the coherence and consistency of the generated stories, resulting in engaging and easily comprehensible narratives.
+However, many children often consume stories passively, missing out on the opportunity to participate in the creative process.
+To address this, we propose a storytelling system that creates adventure-type stories with multiple branches that users can explore.
+We generate these interactive stories using a character drawing as input, with visual features extraction using GPT-4.
+By leveraging LLM hallucinations, we generate interactive stories using user feedback as a prompt.
+Finally, we refine the quality of the generated story through a complexity analysis algorithm.
+We believe that the use of a drawing as input further improves the engagement in the story and characters.
 \end{abstract}

### 2023-12-22 paper_interaction_conf/main.tex
This commit adds a system overview figure to the main.tex file.
updated intro

@@
 \label{sec:introduction}
-
 Creativity is increasingly recognized as a crucial aspect of the modern working environment.
@@
 As a result, there has been a growing interest in leveraging creative artificial intelligence (AI) and exploring the use of AI agents to stimulate children's creativity.
-Previous research has demonstrated the positive effects of incorporating AI agents with creative abilities in enhancing children's creative thinking \cite{1:ElgarfP22}.
+Previous research has demonstrated the positive effects of incorporating AI agents with creative abilities in enhancing children's creative thinking.
 Additionally, the use of storytelling robots and virtual characters as interactive tools has gained traction in recent years \cite{7:SunLLL17}.
-These advancements highlight the potential of AI technologies in promoting and nurturing creativity in children, thereby shaping their cognitive and emotional development.
+In this paper, we propose \textit{MyStoryKnight}, an interactive AI tool for generating stories.
 
-One effective way to promote creativity is through storytelling, a popular activity for entertaining and bonding with children \cite{7:SunLLL17}.
-Storytelling plays a crucial role in child development \cite{9:RyokaiC99} and offers several ultiple benefits \cite{7:SunLLL17}.
-Both story-making and storytelling contribute to the development of verbal and social skills \cite{1:ElgarfP22}, and recent research suggests that storytelling broadens vocabulary, improves narrative comprehension, and accelerates cognitive development in children \cite{7:SunLLL17}.
-Creating fictional worlds and characters helps children improve their language skills, both in comprehension and usage \cite{13:abs-2011-04242}.
+Our proposed system is intended to promote children's creativity through storytelling, a popular activity for entertaining and bonding \cite{7:SunLLL17}.
+Both storymaking and storytelling contribute to the development of verbal and social skills \cite{9:RyokaiC99}, such as broadening the vocanulary and improving  narrative comprehension.
+Besides, creating fictional worlds and characters helps children improve their language skills, both in comprehension and usage \cite{13:abs-2011-04242}.
+In \textit{MyStoryKnight}, users, together with an AI, co-create stories with multiple explorable branches.
 
-Collaborative storytelling has been shown to be an effective way of building and strengthening relationships \cite{8:ShakeriND21}, also playing an important role in parent-child bonding \cite{12:ZhangXWYRWYWL22}.
-Interactive stories stimulate children's thinking and imagination \cite{11:LimaGV20}, and help children make sense of their world through shared experiences \cite{9:RyokaiC99}.
-Despite these benefits, many parents do not regularly engage in interactive storytelling with their children due to limited availability, time, or energy [7, 12].
-
-To address this, we propose \textbf{MyStoryKnight}, a character drawing driven storytelling system that uses LLM hallucinations to generate an adventure-type story with user agency and navigation.
+Despite all the benefits of practicing storytelling, many children do not have the opportunity to engage in interactive storytelling.
+\textit{MyStoryKnight} addresses this problem by generating an adventure-type story through LLM hallucinations.
+Figure \ref{fig:system-overview}  shows an overview of our system.
 Our system uses drawings of characters as input, and generates an unfolding story that the user can navigate through based on their choices.
@@
 Resulting in a story that is both engaging and easy to follow.
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/1920x720px.png}
+    \caption{MyStoryKnight system overview.}
+    \label{fig:system-overview}
+\end{figure*}
 

### 2023-12-22 paper_interaction_conf/main.tex
Reshape related work section

--- 2023-12-22 paper_interaction_conf/main.tex
@@
 To address this, we propose \textbf{MyStoryKnight}, a character drawing driven storytelling system that uses LLM hallucinations to generate an adventure-type story with user agency and navigation.
+Figure \ref{fig:system-overview} shows an overview of our system.
 Our system uses drawings of characters as input, and generates an unfolding story that the user can navigate through based on their choices.
@@
 
-Previous works have explored using interactive dialogue to develop congruent stories, utilizing online information to enrich narratives \cite{13:abs-2011-04242}, creating storytelling experiences with interactive questioning and answering through collaboration between parents and AI \cite{12:ZhangXWYRWYWL22}, and input and personalization have been used to make stories more engaging and informative \cite{14:WangRCRMB22}.
-Research has also focused on enhancing collaborative storytelling between friends and how AI can promote curiosity and discovery by hallucinating new details \cite{8:ShakeriND21}.
-Other studies have considered interaction with existing characters \cite{10:ChopraVSS21}, image-based storytelling with non-verbal prompt generation \cite{4:HanC23}, controlling characters through physical gestures \cite{2:LiuLWCS12}, and physical body engagement \cite{3:ZhaoB23}.
-The possibility of using sketches to influence character behavior or affect the plot of a story, allowing users to interact with narratives by sketching objects, has also been explored \cite{11:LimaGV20}.
-Multi-modal systems, combining oral narration, visual images, and body engagement \cite{3:ZhaoB23}, and systems using user input in the form of prompts to have AI generate high-quality images for story creation \cite{4:HanC23} are also examples of prior works.
+\subsection{Interactive Storytelling}
+Interactive storytelling is a form of storytelling in which the audience is an active participant \cite{14:WangRCRMB22}.
+Interactive storytelling has been shown to be an effective way of building and strengthening relationships \cite{15:SchlauchSG22}, also playing an important role in parent-child bonding \cite{12:ZhangXWYRWYWL22}.
+Interactive stories stimulate thinking and imagination \cite{11:LimaGV20}, and help children make sense of their world through shared experiences \cite{9:RyokaiC99}.
 
-Previous studies suggest that many current interactive AI systems lack the ability to encourage children's enthusiasm.
-It has also been shown that interesting stories often involve narrative shifts and that interactive narratives do not have to be strictly straightforward or logical.
-However, it is crucial to maintain some elements that remain constant, such as character and location descriptions \cite{13:abs-2011-04242}.
+Prior work has explored physical interactivity through the use of tangible objects \cite{9:RyokaiC99} to create stories, and physical gestures to control characters \cite{2:LiuLWCS12} or generate stories \cite{3:ZhaoB23}.
+Other studies have explored the use of sketches to influence character behavior and plot development \cite{11:LimaGV20}.
+However, these studies have not explored the use of character drawings as the driving force behind the story.
 
-Achieving high child engagement is a critical factor in interactive storytelling \cite{12:ZhangXWYRWYWL22}.
-Challenges in interactive storytelling include the difficulty of maintaining a child's attention, especially when there is little change in activities or interaction patterns \cite{13:abs-2011-04242}.
-Narrators must respond in a way that keeps the child interested while maintaining the narrative trajectory.
-Children quickly become bored and distracted, and in terms of storytelling, it's an issue that becomes more problematic when the parent is not present \cite{12:ZhangXWYRWYWL22}.
-Another crucial factor in storytelling is the story characters, and providing users with the possibility to interact with characters can offer a more immersive and informative experience \cite{10:ChopraVSS21}.
-Interactivity and authorship, where computational methods allow users to participate in story creation, are fundamental aspects of interactive storytelling \cite{11:LimaGV20}.
+\subsection{AI Storytelling}
+AI usage has been experiencing a surge in popularity in recent years, with many applications in the creative arts.
+Generative AI especially has the potential to contribute to creative processes \cite{6:TholanderJ23}.
+One such creative process could be storytelling.
+Prior work has explored how generative AI can be used to create stories \cite{13:abs-2011-04242}, and even collaborate in story generation with humans \cite{8:ShakeriND21}.
+Other studies explored how generative AI can be used to expand existing story worlds \cite{10:ChopraVSS21}, or generate multi-modal storytelling experiences \cite{4:HanC23}.
+However, while consistency and coherency are essential in storytelling, they are often overlooked in AI-generated stories.
+
+\subsection{Storytelling with Children}
+Children oriented storytelling has been explored widely in the past.
+Prior work has explored the use of robots as storytelling companions \cite{7:SunLLL17}, and the use of virtual characters to promote collaboreation \cite{2:LiuLWCS12}.
+Other studies have explored the use of AI agents to stimulate children's creativity \cite{1:ElgarfP22}.
+Other studies have shown how AI can support parent-child bonding \cite{12:ZhangXWYRWYWL22}, and encourage physical interaction and play \cite{3:ZhaoB23}.
+However, utilizing hallucinations to generate stories has not been explored in the context of user-agency for storytelling with children.
 

### 2023-12-22 paper_interaction_conf/main.tex

@@
 As a result, there has been a growing interest in leveraging creative artificial intelligence (AI) and exploring the use of AI agents to stimulate children's creativity.
-Previous research has demonstrated the positive effects of incorporating AI agents with creative abilities in enhancing children's creative thinking \cite{1:ElgarfP22}.
+Previous research has demonstrated the positive effects of incorporating AI agents with creative abilities in enhancing children's creative thinking.
 Additionally, the use of storytelling robots and virtual characters as interactive tools has gained traction in recent years \cite{7:SunLLL17}.
-These advancements highlight the potential of AI technologies in promoting and nurturing creativity in children, thereby shaping their cognitive and emotional development.
+In this paper, we propose \textit{MyStoryKnight}, an interactive AI tool for generating stories.
 
-One effective way to promote creativity is through storytelling, a popular activity for entertaining and bonding with children \cite{7:SunLLL17}.
-Storytelling plays a crucial role in child development \cite{9:RyokaiC99} and offers several ultiple benefits \cite{7:SunLLL17}.
-Both story-making and storytelling contribute to the development of verbal and social skills \cite{1:ElgarfP22}, and recent research suggests that storytelling broadens vocabulary, improves narrative comprehension, and accelerates cognitive development in children \cite{7:SunLLL17}.
-Creating fictional worlds and characters helps children improve their language skills, both in comprehension and usage \cite{13:abs-2011-04242}.
+Our proposed system is intended to promote children's creativity through storytelling, a popular activity for entertaining and bonding \cite{7:SunLLL17}.
+Both storymaking and storytelling contribute to the development of verbal and social skills \cite{9:RyokaiC99}, such as broadening the vocanulary and improving  narrative comprehension.
+Besides, creating fictional worlds and characters helps children improve their language skills, both in comprehension and usage \cite{13:abs-2011-04242}.
+In \textit{MyStoryKnight}, users, together with an AI, co-create stories with multiple explorable branches.
 
-Collaborative storytelling has been shown to be an effective way of building and strengthening relationships \cite{8:ShakeriND21}, also playing an important role in parent-child bonding \cite{12:ZhangXWYRWYWL22}.
-Interactive stories stimulate children's thinking and imagination \cite{11:LimaGV20}, and help children make sense of their world through shared experiences \cite{9:RyokaiC99}.
-Despite these benefits, many parents do not regularly engage in interactive storytelling with their children due to limited availability, time, or energy [7, 12].
-
-To address this, we propose \textbf{MyStoryKnight}, a character drawing driven storytelling system that uses LLM hallucinations to generate an adventure-type story with user agency and navigation.
+Despite all the benefits of practicing storytelling, many children do not have the opportunity to engage in interactive storytelling.
+\textit{MyStoryKnight} addresses this problem by generating an adventure-type story through LLM hallucinations.
 Figure \ref{fig:system-overview}  shows an overview of our system.

### 2023-12-22 paper_interaction_conf/main.tex
Add references to support the benefits of storytelling in promoting children's creativity

@@
 Our proposed system is intended to promote children's creativity through storytelling, a popular activity for entertaining and bonding \cite{7:SunLLL17}.
-Both storymaking and storytelling contribute to the development of verbal and social skills \cite{9:RyokaiC99}, such as broadening the vocanulary and improving  narrative comprehension.
+Both storymaking and storytelling contribute to the development of verbal and social skills \cite{9:RyokaiC99,5:CurrinDPCFGH23}, such as broadening the vocanulary and improving  narrative comprehension.
 Besides, creating fictional worlds and characters helps children improve their language skills, both in comprehension and usage \cite{13:abs-2011-04242}.

### 2023-12-22 paper_interaction_conf/main.tex
Add new references and update system architecture and user interface

@@
 \usepackage{latexsym}
+\usepackage{url}
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/1920x720px.png}
+    \includegraphics[width=0.9\textwidth]{figures/2400x600px.png}
     \caption{MyStoryKnight system overview.}
@@
 \section{System Overview}
+\label{sec:system-overview}
+To address these issues, we designed \textbf{MyStoryKnight}, an interactive storytelling that uses drawings as input and utilizes LLM hallucinations to generate a branching story.
+Agency is a critical factor in interactive storytelling \cite{11:LimaGV20}, as it promotes engagement and immersion \cite{12:ZhangXWYRWYWL22}.
+Our system supports user agency by allowing users to navigate the story through their choices.
+Additionally, we use a complexity analysis algorithm to guide the LLM hallucinations to generate a coherent and consistent story, fitting for children's comprehension.
+
+\subsection{System Architecture}
+\label{subsec:system-architecture}
+The system architecture is shown in Figure \ref{fig:system-architecture}. The system consists of three main components:
+\begin{enumerate}
+    \item \textbf{Drawing Analysis}: Extracting visual features from the user's drawing.
+The visual features are used as a prompt for the LLM to hallucinate a character description and a background story.
+    \item \textbf{Story Generator}: Story is generated based on user selection on a set of actions. LLM hallucinations are used to generate the story and actions.
+    \item \textbf{Complexity Analysis}: Natural language processing (NLP) techniques are used to analyze the story's coherency and consistency. The results are used to guide the LLM hallucinations.
+\end{enumerate}
+To achieve out goals, we utilize GPT-4 \cite{17:abs-2303-08774} for drawing analysis and story generation.
+Additionally, we use spacy \cite{18:spacy} in addition to GPT-4 for complexity analysis.
+The system is implemented with Django, a Python web framework \cite{19:django}, and React, a JavaScript library for building user interfaces \cite{20:react}.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/800x600px.png}
+    \caption{System architecture.}
+    \label{fig:system-architecture}
+\end{figure}
+
+\section{User Interface}
+\label{sec:user-interface}
+The user interface is shown in Figure \ref{fig:user-interface}. There are three
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/800x600px.png}
+    \caption{User interface.}
+    \label{fig:user-interface}
+\end{figure}
+
+\subsection{Interaction Flow}
+\label{subsec:interaction-flow}
 
 %4
-\section{Implementation}
-
-%5
-\section{Evaluation}
-
-%6
-\section{Discussion}
-
-%7
 \section{Conclusion}

### 2023-12-22 paper_interaction_conf/main.tex
Add OpenAI API and DALL-E references

@@
 \label{sec:user-interface}
-The user interface is shown in Figure \ref{fig:user-interface}. There are three
+The user interface is shown in Figure \ref{fig:user-interface}.
+The main interaction screen consists of an image upload button, an action selector, a reset button, and an output panel.
+The system uses a webcam to scan and identify user drawings which are then uploaded and analyzed.
+The story is them told using speech sythesis with the OpenAI API \cite{21:openai-api}, and story images are generated while mimicing the style of the user.
+Actions are then presented to the user and could be activated by clicking on then, or alternatively by voice commands.
+The user can also choose to restart the story at any point.
 
@@
 \label{subsec:interaction-flow}
+In this section, we describe the interaction flow of the system.
+
+\vspace{10pt} % Add 10pt of vertical spacing
+
+\begin{quote}
+    \textit{Our story begind with a few colord strokes on a piece of paper.}
+\end{quote}
+
+\vspace{10pt} % Add 10pt of vertical spacing
+
+The user draws a character on a piece of paper, and the system scans the drawing using a webcam (Fig. \ref{fig:knight}).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.35\textwidth]{figures/knight.png}
+    \caption{An example of a user drawing. A drawing of a knight, generated with OpenAI's DALL-E \cite{22:dalle}.}
+    \label{fig:knight}
+\end{figure}
+
+The drawing is then uploaded to the system and analyzed. The system then generates a character description and a background story based on the drawing. The background story is then told to the user.
+
+\vspace{10pt} % Add 10pt of vertical spacing
+
+\begin{quote}
+    \textit{Sir Colorful, the most vibrant knight in all the land, is preparing for the Grand Tournament where knights from all across the realms come together to showcase their bravery and skills.
+Each color on Sir Colorfuls armor and shield represents a virtue: blue for loyalty, yellow for generosity, green for hope, and red for courage.
+With his trusty sword and shield, Sir Colorful is ready to face any challenge and make new friends along the way.}
+\end{quote}
+
+\vspace{10pt} % Add 10pt of vertical spacing
+
+The user is then presented with a set of actions to choose from: \verb|Tournament| or \verb|Castle|.
+These choices are then fed into GPT-4 to generate the next part of the story, and the next set of actions.
+The user chooses \verb|Tournament| and the story continues.
+
+\vspace{10pt} % Add 10pt of vertical spacing
+
+\begin{quote}
+    \textit{Excitement bubbled in Sir Colorful's heart as he prepared for the Grand Tournament, where knights from all around would show off their bravery and skills.
+His trusty sword and shield in hand, Sir Colorful was ready to embark on a colorful adventure.
+Which virtue do you think helped him get ready?}
+\end{quote}
+
+\vspace{10pt} % Add 10pt of vertical spacing
+
+This leads to the following actions: \verb|Jousting| and \verb|Dragon hunting|. The user makes their choice and the story continues. This process repeats until the user chooses to end the story.
 
@@
 \section{Conclusion}
+\label{sec:conclusion}
+In this paper, we presented \textit{MyStoryKnight}, an interactive storytelling system that uses character drawings as input.
+We generate an adventure-type story with multiple explorable branches using LLM hallucinations.
+Additionally, we use a complexity analysis algorithm to guide the LLM hallucinations to generate a coherent and consistent story.
+We believe that the use of a drawing as input further improves the engagement in the story and characters.
+In the future we plan to hold a user study to evaluate the effectiveness of our system in promoting creativity and engagement.
 

### 2023-12-23 paper_interaction_conf/main.tex
Update references in paper_interaction_conf and final paper submission vertion v1.6

@@
 %% Interaction 2024 Technical Report Submission
-%% V1.0 (2023/12/22)
+%% V1.6 (2023/12/22)
 %%
@@
 
-\author{Yotam Sechayk}{UTokyo}[sechayk-yotam@g.ecc.u-tokyo.ac.jp]
-\author{Gabriela A. Penarska}{TUD,PUTokyo}[gabriela-penarska@g.ecc.u-tokyo.ac.jp]
-\author{Isa A. Randsalu}{LU,PUTokyo}[randsalu-isa071@g.ecc.u-tokyo.ac.jp]
-\author{Christian Arzate Cruz}{HRI}[]
-
-\author{Takeo Igarashi}{UTokyo}[]
+\author{Sechayk Yotam}{UTokyo}[sechayk-yotam@g.ecc.u-tokyo.ac.jp]
+\author{Penarska Gabriela A.}{TUD,PUTokyo}[gabriela-penarska@g.ecc.u-tokyo.ac.jp]
+\author{Randsalu Isa A.}{LU,PUTokyo}[randsalu-isa071@g.ecc.u-tokyo.ac.jp]
+\author{Arzate Cruz Christian}{HRI}[]
+\author{Igarashi Takeo}{UTokyo}[]
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/2400x600px.png}
-    \caption{MyStoryKnight system overview.}
+    \includegraphics[width=0.95\textwidth]{figures/system-overview.png}
+    \caption{MyStoryKnight system overview. Drawing is anaylzed with GPT-4. Backstory and action choices are presented to the user. Story unfolds based on user choice.}
     \label{fig:system-overview}
@@
 \label{sec:system-overview}
-To address these issues, we designed \textbf{MyStoryKnight}, an interactive storytelling that uses drawings as input and utilizes LLM hallucinations to generate a branching story.
+We designed \textbf{MyStoryKnight}, an interactive storytelling that uses drawings as input and utilizes LLM hallucinations to generate a branching story.
 Agency is a critical factor in interactive storytelling \cite{11:LimaGV20}, as it promotes engagement and immersion \cite{12:ZhangXWYRWYWL22}.
@@
 \label{subsec:system-architecture}
-The system architecture is shown in Figure \ref{fig:system-architecture}. The system consists of three main components:
+The system consists of three main components:
 \begin{enumerate}
@@
 The visual features are used as a prompt for the LLM to hallucinate a character description and a background story.
-    \item \textbf{Story Generator}: Story is generated based on user selection on a set of actions. LLM hallucinations are used to generate the story and actions.
+    \item \textbf{Story Generator}: Story is generated based on user selection on a set of actions. LLM hallucinations are used to generate both the story and actions.
     \item \textbf{Complexity Analysis}: Natural language processing (NLP) techniques are used to analyze the story's coherency and consistency. The results are used to guide the LLM hallucinations.
 \end{enumerate}
-To achieve out goals, we utilize GPT-4 \cite{17:abs-2303-08774} for drawing analysis and story generation.
+To achieve our goals, we utilize GPT-4 \cite{17:abs-2303-08774} for drawing analysis and story generation.
 Additionally, we use spacy \cite{18:spacy} in addition to GPT-4 for complexity analysis.
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/800x600px.png}
-    \caption{System architecture.}
-    \label{fig:system-architecture}
-\end{figure}
-
 \section{User Interface}
 \label{sec:user-interface}
+
 The user interface is shown in Figure \ref{fig:user-interface}.
-The main interaction screen consists of an image upload button, an action selector, a reset button, and an output panel.
-The system uses a webcam to scan and identify user drawings which are then uploaded and analyzed.
-The story is them told using speech sythesis with the OpenAI API \cite{21:openai-api}, and story images are generated while mimicing the style of the user.
-Actions are then presented to the user and could be activated by clicking on then, or alternatively by voice commands.
-The user can also choose to restart the story at any point.
+The main interaction screen consists of an action selection area (bottom), a restart button (top-right), a microphone indication toggle (bottom-left), and a story output panel (center).
 
-\begin{figure}[t]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=0.45\textwidth]{figures/800x600px.png}
-    \caption{User interface.}
+    \includegraphics[width=0.45\textwidth]{figures/user-interface.png}
+    \caption{Mockup of the user interface.}
     \label{fig:user-interface}
@@
 
-\subsection{Interaction Flow}
-\label{subsec:interaction-flow}
+The system uses a webcam to scan and identify user drawings which are then uploaded and analyzed.
+The story is then told using speech synthesis with the OpenAI API \cite{21:openai-api}, and story images are generated using DALL-E \cite{22:dalle}.
+The generated images are optimized to maintain a style similar to that of the user.
+Actions are then presented to the user, and these could be activated by clicking, or alternatively by voice commands.
+The user can also choose to restart the story at any point.
+
+\section{Experiencing MyStoryKnight}
+\label{subsec:using-mystoryknight}
 In this section, we describe the interaction flow of the system.
@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \includegraphics[width=0.35\textwidth]{figures/knight.png}
+    \includegraphics[width=0.3\textwidth]{figures/knight.png}
     \caption{An example of a user drawing. A drawing of a knight, generated with OpenAI's DALL-E \cite{22:dalle}.}
@@
 \begin{quote}
-    \textit{Sir Colorful, the most vibrant knight in all the land, is preparing for the Grand Tournament where knights from all across the realms come together to showcase their bravery and skills.
+    \textit{Sir Colorful, the most vibrant knight in all the land.
 Each color on Sir Colorfuls armor and shield represents a virtue: blue for loyalty, yellow for generosity, green for hope, and red for courage.
-With his trusty sword and shield, Sir Colorful is ready to face any challenge and make new friends along the way.}
+With his trusty sword and shield, Sir Colorful is ready to face any challenge.}
 \end{quote}
@@
 
-The user is then presented with a set of actions to choose from: \verb|Tournament| or \verb|Castle|.
+The user is then presented with a set of actions to choose from: \verb|Go to tournament| or \verb|Run away|.
 These choices are then fed into GPT-4 to generate the next part of the story, and the next set of actions.
-The user chooses \verb|Tournament| and the story continues.
+The user chooses \verb|Go to tournament| and the story continues (Fig.
+\ref{fig:tournament}).
 
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.35\textwidth]{figures/tournament-hall.png}
+    \caption{An example output of the system, the \'tournament hall\'. Generated with OpenAI's DALL-E \cite{22:dalle}.}
+    \label{fig:tournament}
+\end{figure}
+
 \begin{quote}
-    \textit{Excitement bubbled in Sir Colorful's heart as he prepared for the Grand Tournament, where knights from all around would show off their bravery and skills.
-His trusty sword and shield in hand, Sir Colorful was ready to embark on a colorful adventure.
-Which virtue do you think helped him get ready?}
+    \textit{The tournament hall was filled with knights from all across the realms, each one more colorful than the last.
+Sir Colorful was eager to make new friends and show off his skills.
+But first he had to comence his training.}
 \end{quote}
@@
 
-This leads to the following actions: \verb|Jousting| and \verb|Dragon hunting|. The user makes their choice and the story continues. This process repeats until the user chooses to end the story.
+This leads to the following actions: \verb|Jousting| and \verb|Weight lifting|. The user makes their choice and the story continues. This process repeats until the user chooses to end the story.
 
@@
 % Acknowledgment
-\begin{acknowledgment}
-    Test.
-\end{acknowledgment}
+% \begin{acknowledgment}
+% \end{acknowledgment}
 
@@
 % Appendix
-\appendix
+% \appendix
 

### 2023-12-24 backend/llm.py
Add new functionality and update dependencies

@@ -39,6 +39,9 @@ class LLMStoryteller:
             self.llm = OpenAILLM()
             self.model = config["openai"]["model"]
             self.vmodel = config["openai"]["vmodel"]
+            self.vgen = config["openai"]["vgen"]
+            self.stt = config["openai"]["stt"]
+            self.tts = config["openai"]["tts"]
             logger.info(f"LLM storyteller initialized with model={self.model}")
         else:
             logger.error(f"LLM type {config['llm']['type']} is not implemented")
@@ -52,6 +55,17 @@ class LLMStoryteller:
             {"role": "user", "content": "Hello, who are you?"},
         ]
         return self.send_llm_request(messages)
+
+    def generate_story_image(self, prompt):
+        response = self.llm().images.generate(
+            model=self.vgen,
+            prompt=prompt,
+            size="1024x1024",
+            quality="standard",
+            n=1,
+        )
+        image_url = response.data[0].url
+        return image_url
 
     def generate_story_part(self, prompt):
         # Send LLM request to generate a story based on the given prompt
@@ -72,6 +86,16 @@ class LLMStoryteller:
     def calc_story_part_score(self, story_part):
         # Get the score of a story part
         pass
+
+    def transcribe_audio(self, audio):
+        audio_file = open(audio, "rb")
+        transcript = self.llm().audio.transcriptions.create(
+            model=self.stt,
+            file=audio_file,
+            response_format="verbose_json",
+            language="en",
+        )
+        return transcript.model_dump_json(indent=4)
 
     def __get_least_frequenct_word(self, story_part):
         # Get the least frequent word in the story part

### 2023-12-24 paper_interaction_conf/main.tex
Update references in references.bib and main.bbl files and add ne sections to main.tex

@@
 \end{enumerate}
-To achieve our goals, we utilize GPT-4 \cite{17:abs-2303-08774} for drawing analysis and story generation.
-Additionally, we use spacy \cite{18:spacy} in addition to GPT-4 for complexity analysis.
-The system is implemented with Django, a Python web framework \cite{19:django}, and React, a JavaScript library for building user interfaces \cite{20:react}.
+To achieve our goals, we utilize GPT-4 \cite{16:abs-2303-08774} for drawing analysis and story generation.
+Additionally, we use spacy \cite{17:spacy} in addition to GPT-4 for complexity analysis.
+The system is implemented with Django, a Python web framework \cite{18:django}, and React, a JavaScript library for building user interfaces \cite{19:react}.
+
+\subsection{Drawing Analysis}
+\label{subsec:drawing-analysis}
+Using prompt engineering methods \cite{22:abs-2302-11382}, we extract visual features, such as colors and detected elemments, from the user's drawing.
+We then generate a backstory for the character with consideration to the recognized visual features (Tab.
+\ref{tab:drawing-analysis}).
+
+\begin{table}[h]
+    \centering
+    \caption{Sample of drawing analysis output.}
+    \label{tab:drawing-analysis}
+    \hbox to\hsize{\hfil
+        \begin{tabular}{|l|p{0.65\linewidth}|}
+            \hline
+            \textbf{Description}   & A drawing of a knight in colorful armor holding a sword and shield.
+\\
+            \hline
+            \textbf{Items}         & knight, sword, shield, helmet, armor                                                                                                                                                                                                                                                  \\
+            \hline
+            \textbf{Colors}        &
+            \begin{tabular}[c]{@{}l@{}}
+                - grey (usage: the sword and helmet)       \\
+                - blue and yellow (usage: shield sections) \\
+                - green (usage: part of the armor)         \\
+                - red (usage: part of the armor)           \\
+                - brown (usage: belt and boots)
+            \end{tabular}                                                                                                                                                                                                                                                                     \\
+            \hline
+            \textbf{Relationships} &
+            \begin{tabular}[c]{@{}l@{}}
+                - sword: held in the knight's right hand \\
+                - shield: held in the knight's left hand
+            \end{tabular}                                                                                                                                                                                                                                                                       \\
+            \hline
+            \textbf{Story}         & Sir Colorful, the most vibrant knight in all the land.
+Each color on Sir Colorfuls armor and shield represents a virtue: blue for loyalty, yellow for generosity, green for hope, and red for courage.
+With his trusty sword and shield, Sir Colorful is ready to face any challenge.
+\\
+            \hline
+        \end{tabular}\hfil}
+\end{table}
+
+\subsection{Story Generation}
+\label{subsec:story-generation}
+The story is generated using LLM hallucinations.
+The LLM hallucinations are guided by the user's choices, as well as the complexity analysis algorithm (Sec.
+\ref{subsec:complexity-analysis}), which is used to ensure the coherency and consistency of the story.
+The story is generated in parts, including a set of actions.
+The user can choose one of the actions, which leads to the next part of the story.
+
+The story continues until one of the ending criterias are met:
+\begin{enumerate}
+    \item The user chooses to end the story.
+    \item The story reaches a maximum number of parts.
+\end{enumerate}
+
+\subsection{Complexity Analysis}
+\label{subsec:complexity-analysis}
+To enhance the quality of the generated story, we have devised a plan that includes the following steps:
+
+\begin{itemize}
+    \item \textbf{Object and Entity Tracking:}
+          We will utilize NLP techniques to track and identify objects, people, and places mentioned in the story. This will allow us to maintain consistency and coherence throughout the narrative.
+
+    \item \textbf{Comparison with Existing Knowledge:}
+          We will compare the new story elements with the knowledge established in the previous parts of the story.
+By considering the differences, we can ensure that the new elements are integrated smoothly into the narrative.
+
+    \item \textbf{Word Frequency Analysis:}
+          We will analyze the mean word frequency as well as the maximum and minimum word frequency in each new story part.
+This analysis will help us avoid using too many uncommon words, ensuring that the story remains accessible and engaging for the target audience.
+
+    \item \textbf{Tracking New Story Elements:}
+          We will keep track of the number of new story elements introduced in each new story part.
+This will allow us to control the introduction of new elements and maintain a balance between familiarity and novelty in the story.
+\end{itemize}
+
+In order to create a compelling story, we will adhere to the following principles:
+
+\begin{enumerate}
+    \item \textbf{Consistency in Storytelling:} We will not abandon any item or element introduced in the story without a valid reason.
+This will ensure that all story elements contribute to the overall narrative and maintain coherence.
+    \item \textbf{Language Accessibility:} We will avoid using an excessive number of uncommon words.
+By keeping the language accessible, we will ensure that the story is easily understood and enjoyed by the target audience.
+    \item \textbf{Controlled Introduction of New Elements:} We will be mindful of introducing too many new story elements in each part.
+This will prevent overwhelming the audience and allow them to engage with and comprehend the story effectively.
+\end{enumerate}
 
@@
 The system uses a webcam to scan and identify user drawings which are then uploaded and analyzed.
-The story is then told using speech synthesis with the OpenAI API \cite{21:openai-api}, and story images are generated using DALL-E \cite{22:dalle}.
+The story is then told using speech synthesis with the OpenAI API \cite{20:openai-api}, and story images are generated using DALL-E \cite{21:dalle}.
 The generated images are optimized to maintain a style similar to that of the user.
@@
     \includegraphics[width=0.3\textwidth]{figures/knight.png}
-    \caption{An example of a user drawing. A drawing of a knight, generated with OpenAI's DALL-E \cite{22:dalle}.}
+    \caption{An example of a user drawing. A drawing of a knight, generated with OpenAI's DALL-E \cite{21:dalle}.}
     \label{fig:knight}
@@
     \includegraphics[width=0.35\textwidth]{figures/tournament-hall.png}
-    \caption{An example output of the system, the \'tournament hall\'. Generated with OpenAI's DALL-E \cite{22:dalle}.}
+    \caption{An example output of the system, the \'tournament hall\'. Generated with OpenAI's DALL-E \cite{21:dalle}.}
     \label{fig:tournament}
@@
 
-This leads to the following actions: \verb|Jousting| and \verb|Weight lifting|. The user makes their choice and the story continues. This process repeats until the user chooses to end the story.
+This leads to the following actions: \verb|Jousting| and \verb|Weight lifting|.
+The user makes their choice and the story continues.
+This process repeats until the user chooses to end the story or the story reaches a maximum number of parts.
 

### 2023-12-24 paper_interaction_conf/main.tex
Refactor interactive storytelling and AI storytelling sections
Add details about the system implementation and user interface

@@
 Interactive storytelling is a form of storytelling in which the audience is an active participant \cite{14:WangRCRMB22}.
-Interactive storytelling has been shown to be an effective way of building and strengthening relationships \cite{15:SchlauchSG22}, also playing an important role in parent-child bonding \cite{12:ZhangXWYRWYWL22}.
+Interactive storytelling has been shown to be an effective way of building and strengthening relationships \cite{15:SchlauchSG22}, playing an important role in parent-child bonding \cite{12:ZhangXWYRWYWL22}.
 Interactive stories stimulate thinking and imagination \cite{11:LimaGV20}, and help children make sense of their world through shared experiences \cite{9:RyokaiC99}.
 
-Prior work has explored physical interactivity through the use of tangible objects \cite{9:RyokaiC99} to create stories, and physical gestures to control characters \cite{2:LiuLWCS12} or generate stories \cite{3:ZhaoB23}.
+Prior work has explored physical interactivity through the use of tangible objects to create stories \cite{9:RyokaiC99}, and physical gestures to control characters \cite{2:LiuLWCS12} or create stories \cite{3:ZhaoB23}.
 Other studies have explored the use of sketches to influence character behavior and plot development \cite{11:LimaGV20}.
-However, these studies have not explored the use of character drawings as the driving force behind the story.
+
+However, these studies have not explored the use of tangible character drawings made by users as the driving force behind the story.
 
@@
 One such creative process could be storytelling.
-Prior work has explored how generative AI can be used to create stories \cite{13:abs-2011-04242}, and even collaborate in story generation with humans \cite{8:ShakeriND21}.
-Other studies explored how generative AI can be used to expand existing story worlds \cite{10:ChopraVSS21}, or generate multi-modal storytelling experiences \cite{4:HanC23}.
+
+Prior work has explored how generative AI can be used to create stories \cite{13:abs-2011-04242}, and even collaborate in story generation with other humans \cite{8:ShakeriND21}.
+Other studies explored how generative AI can be used to expand existing story worlds \cite{10:ChopraVSS21}, or generate comprehensive multi-modal storytelling experiences \cite{4:HanC23}.
+
 However, while consistency and coherency are essential in storytelling, they are often overlooked in AI-generated stories.
@@
 \subsection{Storytelling with Children}
-Children oriented storytelling has been explored widely in the past.
-Prior work has explored the use of robots as storytelling companions \cite{7:SunLLL17}, and the use of virtual characters to promote collaboreation \cite{2:LiuLWCS12}.
-Other studies have explored the use of AI agents to stimulate children's creativity \cite{1:ElgarfP22}.
-Other studies have shown how AI can support parent-child bonding \cite{12:ZhangXWYRWYWL22}, and encourage physical interaction and play \cite{3:ZhaoB23}.
-However, utilizing hallucinations to generate stories has not been explored in the context of user-agency for storytelling with children.
+Children oriented storytelling has been widely explored in the past.
+Prior work has examimned the use of robots as storytelling companions \cite{7:SunLLL17}, and the use of virtual characters to promote collaboreation \cite{2:LiuLWCS12}.
+Other studies have explored the use of AI agents to stimulate children's creativity \cite{1:ElgarfP22}, or show how AI can support parent-child bonding \cite{12:ZhangXWYRWYWL22}.
+Moreover, storytelling with AI-agents can encourage physical interaction and play \cite{3:ZhaoB23}.
+
+However, utilizing LLM hallucinations to generate stories has not been explored in the context of user-agency for storytelling with children.
 
@@
 To achieve our goals, we utilize GPT-4 \cite{16:abs-2303-08774} for drawing analysis and story generation.
-Additionally, we use spacy \cite{17:spacy} in addition to GPT-4 for complexity analysis.
+Additionally, we use spacy \cite{17:spacy} in addition to the former for complexity analysis.
 The system is implemented with Django, a Python web framework \cite{18:django}, and React, a JavaScript library for building user interfaces \cite{19:react}.
@@
 Using prompt engineering methods \cite{22:abs-2302-11382}, we extract visual features, such as colors and detected elemments, from the user's drawing.
-We then generate a backstory for the character with consideration to the recognized visual features (Tab.
-\ref{tab:drawing-analysis}).
+We then generate a backstory for the character with consideration to the recognized visual features.
+Table \ref{tab:drawing-analysis} shows an exammple output for the input in Figure \ref{fig:knight}.
 
@@
 The story is generated using LLM hallucinations.
-The LLM hallucinations are guided by the user's choices, as well as the complexity analysis algorithm (Sec.
-\ref{subsec:complexity-analysis}), which is used to ensure the coherency and consistency of the story.
-The story is generated in parts, including a set of actions.
+The LLM hallucinations are guided by the user's choices, as well as the complexity analysis algorithm (Section \ref{subsec:complexity-analysis}), which is used to ensure the coherency and consistency of the story.
+The story is generated in parts, alongside a set of actions.
 The user can choose one of the actions, which leads to the next part of the story.
 
-The story continues until one of the ending criterias are met:
+The story continues until one of the following ending criteria is met:
 \begin{enumerate}
@@
 The generated images are optimized to maintain a style similar to that of the user.
-Actions are then presented to the user, and these could be activated by clicking, or alternatively by voice commands.
+Actions are then presented to the user, and these could be activated by clicking, or alternatively using voice commands.
 The user can also choose to restart the story at any point.
